Language-Based Security for Low-Level MPC

### 2024-05-17 ppdp24/intro.tex
checkpoint
tiny tweaks and a note

Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern, distributed applications such as privacy-preserving
machine learning \cite{li2021privacy, knott2021crypten,
  koch2020privacy, liu2020privacy} and Zero-Knowledge proofs in
blockchains \cite{ishai2009zero, lu2019honeybadgermpc,
  gao2022symmeproof, tomaz2020preserving}. MPC methods have been
developed by the cryptography community for many years, while
receiving the attention of the programming languages community more
recently. In contrast, information flow security has received
significant attention in PL theory and practice especially since the
turn of the century \cite{1159651}, including a menagerie of variants,
enforcement mechanisms, and programming frameworks. Much of this has
been enabled by the unified metatheory of \emph{hyperproperties}
\cite{10.5555/1891823.1891830}, including noninterference, that
establishes a common conceptual framework for reasoning about and
implementing systems with information flow security.

@@

>>>>

Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern, distributed applications such as privacy-preserving
machine learning \cite{li2021privacy, knott2021crypten,
  koch2020privacy, liu2020privacy} and Zero-Knowledge proofs in
blockchains \cite{ishai2009zero, lu2019honeybadgermpc,
  gao2022symmeproof, tomaz2020preserving}. The security semantics of
MPC include both confidentiality and integrity properties incorporated
into models such as real/ideal (aka simulator) security and universal
composability (UC), developed primarily by the cryptography community
\cite{XXX}.  Related proof methods are well-studied \cite{Lindell2017}
but mostly manual. Somewhat independently, a significant
body of work in programming languages has focused on definition and
enforcement of confidentiality and integrity \emph{hyperproperties}
\cite{10.5555/1891823.1891830} such as noninterference and delimited
release \cite{XXX}. But following a tradition of connecting
cryptographic and PL-based security models \cite{XXX}, recent work has
also recognized connections between MPC security models and
hyperpoperties of, e.g., noninterference \cite{XXX}, and even
leveraged these connections to enforce MPC security through mechanisms
such as security types \cite{XXX}. Major benefits of this connection
in an MPC setting include better language abstractions for defining
protocols and for mechanisation and even automation of security proofs.

The goal of this paper is to develop a PL model for defining a variety of
low-level probabilistic MPC protocols, to formulate a collection
of confidentiality and integrity hyperproperties for our model
model with familiar information flow analogs, and to show how these
properties can be leveraged for improved proof automation.

The distinction between high- and low-level languages for MPC is
important. High-level languages such as Wysteria \cite{XXX} and
Viaduct \cite{XXX} are designed to provide effective programming of
full applications. These language designs incorporate sophisticated
verified compilation techniques such as orchestration \cite{XXX} to
guarantee high-level security properties, and they rely on
\emph{libraries} of low-level MPC protocols, such as binary and
arithmetic circuits. These low-level protocols encapsulate
abstractions such as secret sharing and semi-homomorphic encrypytion,
and rely on probabilistic progamming methods. So, low-level MPC
programming and protocol verification is a distinct challenge but
critical to the general challenge of PL design for MPC, and complementary
to high-level language design.

Analysis of

have been developed

The security
threat models and engMPC is mainly the
product of a significant body of work in cryptography,

information flow security has received
significant attention in PL theory and practice especially since the
turn of the century \cite{1159651}, including a menagerie of variants,
enforcement mechanisms, and programming frameworks. Much of this has
been enabled by the unified metatheory of \emph{hyperproperties}
\cite{10.5555/1891823.1891830}, including noninterference, that
establishes a common conceptual framework for reasoning about and
implementing systems with information flow security.

@@

\compfig
